From Object Classification to Naming: Modeling Entry-level Names for Real-world Objects

### 2019-12-08 papers/ACL2020/analysis.tex
new TABLE, with human-like errors

\gbt{To do: better structure content into subsections. Decide which results to report. Adapt text.}

\begin{table*}[t]
	\centering
	\small
	\begin{tabular}{l|c|r@{~}r@{~}r@{~}||r@{~}r@{~}r@{~}}
		\toprule
		& & \multicolumn{3}{c}{All Test Images ($\#$)} 
		& \multicolumn{3}{c}{VG$\neq$MN Images ($\#$)}\\
		\toprule
		Model$_{\text{Vocab}}$	& GTtrain  
		&  hit &  correct &  incorrect &  hit &  correct &  wrong \\
		\midrule
		FRCNN$_{\text{VG1600}}$ & VG           &         74.8 &                  13.9 &                    11.3 &         54.3 &                  30.0 &                    15.7 \\
		FRCNN$_{\text{MN442}}$ & VG &         71.1 &                  13.9 &                    15.0 &         48.4 &                  28.7 &                    22.9 \\
		\midrule \midrule
		FRCNN$_{\text{VG1600}}$$_{\text{-VGMN}}$ & MN %&         0.81 &                  0.09 &                    0.11 &         0.60 &                  0.23 &                    0.17 \\
		&         80.7 &                   9.2 &                    10.1 &         60.1 &                  23.8 &                    16.1 \\
		\midrule
		ResNet101$_{\text{MN442}}$ & MN %& 0.70 &                  0.09 &                    0.21 &         0.51 &                  0.22 &                    0.27 \\
		&         69.7 &                  10.3 &                    20.1 &         51.1 &                  23.3 &                    25.6 \\
		ResNet101$_{\text{VGMN}}$ & MN% &         0.69 &                  0.09 &                    0.22 &         0.51 &                  0.23 &                    0.26 \\	
		&         68.7 &                  10.5 &                    20.8 &         50.7 &                  24.2 &                    25.1 \\
		ResNet101$_{\text{VGMN}}$ & VG %&         0.63 &                  0.11 &                    0.26 &         0.31 &                  0.28 &                    0.40 \\
		&         62.8 &                  12.6 &                    24.6 &         31.4 &                  30.0 &                    38.6 \\
		ResNet101$_{\text{MN442}}$ & VG %&         0.64 &                  0.11 &                    0.25 &         0.32 &                  0.29 &                    0.39 \\
		&         63.8 &                  12.6 &                    23.6 &         32.3 &                  30.0 &                    37.7 \\
		\bottomrule
	\end{tabular}
	\caption{Break-down of the results (in \%): Categorization of a predicted name\ $\hat{n}$ into either a \textit{hit} (exact match with entry-level name, cf. standard evaluation), \textit{correct} (less preferred name, synonym, hypernym/hyponym), or \textit{wrong} (wrong object, $\text{count}(\hat{n})<2$, co-hyponym, clear mistake). \label{tab:exp_overview_results}}
\end{table*}

>>>>

The previous Section \ref{}

\begin{table*}[t]
\centering
	\small
\begin{tabular}{ll|rrrr|rrrr|rrrr}
\toprule
&  & \multicolumn{4}{c||}{All objects} & \multicolumn{4}{c||}{MN agreement $>$ 0.9} & \multicolumn{3}{c}{MN agreement $\leq$ 0.9}\\
               model &  GT &  hit &  valid &  err$_{hum}$ &  err &  hit &  valid &   err$_{hum}$ &   err &  hit &  valid &  err$_{hum}$ &  err \\
\midrule
       FRCNN$_{\text{VG1600}}$ &  VG & 74.8 &     13.3 &         7.5 &    4.5 &      94.8 &           0.5 &              2.1 &             2.6 &     63.6 &         20.4 &            10.5 &            5.5 \\
        FRCNN$_{\text{MN442}}$ &  VG & 71.1 &     13.4 &         8.1 &    7.4 &      89.6 &           0.8 &              3.4 &             6.2 &     60.7 &         20.5 &            10.8 &            8.0 \\
 FRCNN$_{\text{VG1600VGMN}}$ &  MN & 80.7 &      8.8 &         7.4 &    3.2 &      94.5 &           0.0 &              4.2 &             1.3 &     72.9 &         13.7 &             9.2 &            4.2 \\
     ResNet101$_{\text{VGMN}}$ &  VG & 62.8 &     11.4 &        15.8 &   10.0 &      88.3 &           0.5 &              5.7 &             5.5 &     48.5 &         17.5 &            21.4 &           12.5 \\
     ResNet101$_{\text{VGMN}}$ &  MN & 68.7 &      9.2 &        13.9 &    8.1 &      89.6 &           0.5 &              4.9 &             4.9 &     57.0 &         14.1 &            19.0 &            9.9 \\
    ResNet101$_{\text{MN442}}$ &  MN & 69.7 &      9.3 &        13.5 &    7.5 &      90.1 &           0.5 &              4.4 &             4.9 &     58.2 &         14.3 &            18.7 &            8.9 \\
    ResNet101$_{\text{MN442}}$ &  VG & 63.8 &     11.6 &        14.8 &    9.8 &      88.6 &           0.8 &              4.4 &             6.2 &     49.9 &         17.6 &            20.7 &           11.8 \\
\bottomrule
\end{tabular}

\caption{New table} \label{tab:humanlike}
\end{table*}
